Simulated Structure Factors

### 2018-07-09 Ben_Manuscripts/fourier_transforms/FT_simple_systems.tex
FT updates + newish figures for poster

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{perfect_crystal_xyz.png}
  \caption{}\label{fig:perfect_crystal_xyz}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{constant_p2p.png}
  \includegraphics[width=0.45\textwidth]{constant_npores.png}
  \caption{The distance between peaks of the structure factor cross-section at
  (0, y, 1.7) is equal to the distance between pores in q-space. The first off-center
  peak of each distribution shows the fundamental frequency. The peaks that follow at 
  higher |$\mathbf{q}$| values are subharmonics. Both systems shown are in unit cells 
  with dimensions of 42.5 x 42.5 x 3.7 nm. (a) The pore-to-pore spacing was held at 
  42.5 nm. The unit cell consists of 100 total pores. The first peak is located at 
  $q_y = .148 \AA^{-1}$ which corresponds to $2\pi / .148 = 42.5 \AA$ in real space. (b)
  We placed four pores in a unit cell spaced 21.25 nm apart. The first peak appears where
  expected at $q_y = 0.0296 \AA^{-1}$ and all other peaks are separated by the same distance.
  }\label{fig:p2p_rpi}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fwhm_fits.png}
  \caption{The gaussian functional form more closely matches the data than the Lorentzian
  functional form. Shown is data for a perfect crystal system with 4 pores and 4 points
  per column.}\label{fig:fwhm_fits}
  \end{figure}

@@

  \begin{table}
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Number of Pores & Distance between Pores &  R-$\pi$ intensity & FWHM ($\AA^{-1}$) \\
  \midrule
  37          &      4            & 212.5                & 200                & 0.372 $\pm$ 0.004 \\ 
  37          &      25           & 85.0                 & 1250               & 0.371 $\pm$ 0.008 \\
  37          &      100          & 42.50                & 5000               & 0.375 $\pm$ 0.013 \\
  \bottomrule
  \end{tabular}
  \caption{We held the size of the unit cell constant at 42.5 x 42.5 x 3.7 nm and varied the
   number of pores and distance between pores. The value of FWHM is indistinguishable between
   the systems.}\label{table:randomly_displaced_columns}
  \end{table}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{one_column_per_pore.png}
  \caption{We placed one column of scatterers at each of 4 pore centers, spaced apart by
  212.5 nm. Since the y-component of the distance between all scatteres is the same in 
  all cases, subharmonics appear just as strongly as the fundamental frequency. Since the 
  intensity doesn't decay, the FWHM is infinite.}\label{fig:infinite_FWHM}
  \end{figure}

@@

  \begin{table}
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores &  R-$\pi$ Intensity\\ 
  \midrule
  14.8        &      4            & 4               & 3.98              \\
  18.5        &      5            & 4               & 5.05              \\
  37          &      10           & 4               & 10.08             \\
  14.8        &      4            & 9               & 4.06              \\
  18.5        &      5            & 9               & 4.78              \\
  37          &      10           & 9               & 10.19             \\
  14.8        &      4            & 16              & 4.01              \\
  18.5        &      5            & 16              & 4.95              \\
  37          &      10           & 16              & 9.61              \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in 
   each column when columns are uncorrelated.}\label{table:randomly_displaced_columns}
  \end{table}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_qy.png}
  \caption{}\label{fig:random_columns_qy}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_rzplot.png}
  \caption{}\label{fig:random_columns_rzplot}
  \end{subfigure}
  \caption{}\label{fig:random_columns_rpi_width}
  \end{figure}

@@

  \begin{table}
  \centering
  \begin{tabular}{c c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores & Number of Atoms & R-$\pi$ Intensity & FWHM $\AA^{-1}$ \\
  \midrule
  14.8        &      4            & 4               & 80              &  80               & 0.37           \\
  18.5        &      5            & 4               & 100             &  100              & 0.37           \\
  37          &      10           & 4               & 200             &  200              & 0.37           \\
  14.8        &      4            & 9               & 180             &  180              & 0.37           \\
  18.5        &      5            & 9               & 225             &  225              & 0.37           \\
  37          &      10           & 9               & 450             &  450              & 0.37           \\
  14.8        &      4            & 16              & 320             &  320              & 0.37           \\
  18.5        &      5            & 16              & 400             &  400              & 0.37           \\
  37          &      10           & 16              & 800             &  800              & 0.37           \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in
   each column when columns are uncorrelated. Note that reproducing these results requires a very fine histogram, 
   and thus a much more expensive calculation. The default binning scheme (100 bins in each dimension) gives slightly
   misleading answers.}\label{table:randomly_displaced_columns}
  \end{table}

@@

  \subsection{Influence of noise}

@@

>>>>

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{perfect_crystal_xyz.png}
  \caption{}\label{fig:perfect_crystal_xyz}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{constant_p2p.png}
  \includegraphics[width=0.45\textwidth]{constant_npores.png}
  \caption{The distance between peaks of the structure factor cross-section at
  (0, y, 1.7) is equal to the distance between pores in q-space. The first off-center
  peak of each distribution shows the fundamental frequency. The peaks that follow at 
  higher |$\mathbf{q}$| values are subharmonics. Both systems shown are in unit cells 
  with dimensions of 42.5 x 42.5 x 3.7 nm. (a) The pore-to-pore spacing was held at 
  42.5 nm. The unit cell consists of 100 total pores. The first peak is located at 
  $q_y = .148 \AA^{-1}$ which corresponds to $2\pi / .148 = 42.5 \AA$ in real space. (b)
  We placed four pores in a unit cell spaced 21.25 nm apart. The first peak appears where
  expected at $q_y = 0.0296 \AA^{-1}$ and all other peaks are separated by the same distance.
  }\label{fig:p2p_rpi}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{fwhm_fits.png}
  \caption{The gaussian functional form more closely matches the data than the Lorentzian
  functional form. Shown is data for a perfect crystal system with 4 pores and 4 points
  per column.}\label{fig:fwhm_fits}
  \end{figure}

@@

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Number of Pores & Distance between Pores &  R-$\pi$ intensity & FWHM ($\AA^{-1}$) \\
  \midrule
  37          &      4            & 212.5                & 200                & 0.372 $\pm$ 0.004 \\ 
  37          &      25           & 85.0                 & 1250               & 0.371 $\pm$ 0.008 \\
  37          &      100          & 42.50                & 5000               & 0.375 $\pm$ 0.013 \\
  \bottomrule
  \end{tabular}
  \caption{We held the size of the unit cell constant at 42.5 x 42.5 x 3.7 nm and varied the
   number of pores and distance between pores. The value of FWHM is indistinguishable between
   the systems.}\label{table:randomly_displaced_columns}
  \end{table}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{one_column_per_pore.png}
  \caption{We placed one column of scatterers at each of 4 pore centers, spaced apart by
  212.5 nm. Since the y-component of the distance between all scatteres is the same in 
  all cases, subharmonics appear just as strongly as the fundamental frequency. Since the 
  intensity doesn't decay, the FWHM is infinite.}\label{fig:infinite_FWHM}
  \end{figure}

@@

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores &  R-$\pi$ Intensity\\ 
  \midrule
  14.8        &      4            & 4               & 3.98              \\
  18.5        &      5            & 4               & 5.05              \\
  37          &      10           & 4               & 10.08             \\
  14.8        &      4            & 9               & 4.06              \\
  18.5        &      5            & 9               & 4.78              \\
  37          &      10           & 9               & 10.19             \\
  14.8        &      4            & 16              & 4.01              \\
  18.5        &      5            & 16              & 4.95              \\
  37          &      10           & 16              & 9.61              \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in 
   each column when columns are uncorrelated.}\label{table:randomly_displaced_columns}
  \end{table}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_qy.png}
  \caption{}\label{fig:random_columns_qy}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{random_columns_rzplot.png}
  \caption{}\label{fig:random_columns_rzplot}
  \end{subfigure}
  \caption{}\label{fig:random_columns_rpi_width}
  \end{figure}

@@

  \begin{table}[!htb]
  \centering
  \begin{tabular}{c c c c c c}
  \toprule
  $L_z$ (\AA) & Points per column & Number of Pores & Number of Atoms & R-$\pi$ Intensity & FWHM $\AA^{-1}$ \\
  \midrule
  14.8        &      4            & 4               & 80              &  80               & 0.37           \\
  18.5        &      5            & 4               & 100             &  100              & 0.37           \\
  37          &      10           & 4               & 200             &  200              & 0.37           \\
  14.8        &      4            & 9               & 180             &  180              & 0.37           \\
  18.5        &      5            & 9               & 225             &  225              & 0.37           \\
  37          &      10           & 9               & 450             &  450              & 0.37           \\
  14.8        &      4            & 16              & 320             &  320              & 0.37           \\
  18.5        &      5            & 16              & 400             &  400              & 0.37           \\
  37          &      10           & 16              & 800             &  800              & 0.37           \\
  \bottomrule
  \end{tabular}
  \caption{The intensity of R-$\pi$ is equal to the number of scatters in
   each column when columns are uncorrelated. Note that reproducing these results requires a very fine histogram, 
   and thus a much more expensive calculation. The default binning scheme (100 bins in each dimension) gives slightly
   misleading answers.}\label{table:randomly_displaced_columns}
  \end{table}

@@

@@

  The pore radius is inversely proportional to the FWHM of systems made with
  randomly rotated layers (See Figure~\ref{fig:pore_radius}). This result is
  not extremely surprsing, although the limits of the relationship suggest 
  that a pore radius of 0 should give an infinite FWHM (supported by Figure
  ~\ref{fig:infinite_FWHM}) and an infinitely large pore radius should have 
  a zero FWHM. This result is also interesting because it suggests that one
  can measure relative pore radii using X-ray diffraction. The difficulty,
  which is associated with the phase problem, is deconvoluting the electron
  density associated with just pore entities.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{pore_radius_FWHM.png}
  \caption{The FWHM decays with increasing pore radius.}\label{fig:pore_radius}
  \end{figure}

%  \begin{table}
%  \centering
%  \begin{tabular}{c c c c c c}
%  \toprule
%  $L_z$ (\AA) &   Pore Radius ($\AA^{-1}$) & FWHM ($\AA^{-1}$)  \\
%  \midrule
%  37          &      1                     &     1.770          \\
%  37          &      2                     &     0.999          \\
%  37          &      3                     &     0.642          \\
%  37          &      4                     &     0.465          \\
%  37          &      5                     &     0.372          \\
%  37          &      7	                   &     0.264          \\
%  37          &      10                    &     0.186          \\
%  37          &      15                    &     0.123          \\
%  \bottomrule
%  \end{tabular}
%  \caption{All systems contain four pores with 5 columns per pore and a unit cell
%  size of 42.5x42.5x3.7 nm. 
%  }\label{table:pore_radius}
%  \end{table}

  \subsection{The influence of thermal disorder}

  We added gaussian noise in each dimension to observe its influence on the intensity
  of R-$\pi$ and the FWHM. For the z-direction, the standard deviation of the 
  gaussian distribution is equal to a fraction of the average distance between scatterers
  in columns. In the xy-directions, the standard deviation is equal to a fraction 
  of the pore radius.

  \subsubsection{Randomly displaced columns}

  When we add noise in the z direction, the intensity of R-$\pi$ decays while the
  FWHM remains infinite.

  When we add noise in the x and y directions, R-$\pi$ has a finite peak width in its 
  $q_y$ dimension. We fit a Gaussian function to the

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{random_columns_gaussian.png}
  \caption{}\label{fig:FWHM_columns}
  \end{figure}
